---
title: "First contact with sparklyr"
author: "Miguel Conde"
date: "16 de diciembre de 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE,
                      fig.align = TRUE)
```

## References
[sparklyr — R interface for Apache Spark][1]
[Deployment and Configuration][2]

## Installation

Install **sparklyr** from CRAN:
```{r}
if (!require("sparklyr")) {
  # install.packages("sparklyr")
  devtools::install_github('rstudio/sparklyr')
  library(sparklyr)
}
```

And a local version of Spark for development purposes:
```{r}
if (nrow(spark_installed_versions()) == 0)
  spark_install(version = "2.1.0")
```
 Pay attention to the IDE's several enhancements for interacting with Spark. You should find a new Spark pane within the IDE. This pane includes a New Connection dialog which can be used to make connections to local or remote Spark instances.
 
## Connecting to Spark

Here we’ll connect to a local instance of Spark:
```{r}
library(sparklyr)
library(dplyr)
sc <- spark_connect(master = "local")
```


## Reading Data

```{r}
library(dplyr)
iris_tbl <- copy_to(sc, iris)
flights_tbl <- copy_to(sc, nycflights13::flights, "flights")
batting_tbl <- copy_to(sc, Lahman::Batting, "batting")
```


[1]: http://spark.rstudio.com/ "sparklyr — R interface for Apache Spark"
[2]: http://spark.rstudio.com/deployment.html "Deployment and Configuration"

